%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Template
% LaTeX Template
% Version 1.0 (December 8 2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Brandon Fryslie
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Authors:
% Sabbir Ahmed, Jeffrey Osazuwa, Howard To, Brian Weber
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[paper=usletter, fontsize=12pt]{article}
\input{structure.tex} % specifies the document layout and style

%----------------------------------------------------------------------------------------

% names
\newcommand{\team}{Galois Field Arithmetic Unit}
\newcommand{\Sabbir}{Sabbir Ahmed}
\newcommand{\Jeffrey}{Jeffrey Osazuwa}
\newcommand{\Howard}{Howard To}
\newcommand{\Brian}{Brian Weber}

% document info command
\newcommand{\documentinfo}[5]{
    \begin{centering}
        \parbox{6.8in}{
        \begin{spacing}{1}
            \begin{flushleft}
                \begin{tabular}{l l}
                    #1 \\
                    #2 \\
                    #3 \\
                    #4 \\
                    #5 \\
                \end{tabular}\\
                \rule{\textwidth}{1pt}
            \end{flushleft}
        \end{spacing}
        }
    \end{centering}
}

\begin{document}

 \documentinfo{\textbf{MEMO NUMBER:} GFAU-SRS}{\textbf{DATE:}  {September 27, 2017}}{\textbf{TO: } EFC LaBerge}{\textbf{FROM: }\Sabbir, \Jeffrey, \Howard, \Brian}{\textbf{SUBJECT: } GFAU Specification Requirements Statement}
    \vspace{-0.3in}


	\section{INTRODUCTION}
		This document servers to enumerate specific requirements of the GFAU.

	\section{BACKGROUND}

The Galois Field Arithmetic Unit (GFAU) is a hardware-based unit for performing arithmetic operations in Galois Field $2^n$, where n = 2 … 10. Unit will accept inputs to determine n, and to establish the field generating polynomial. A GFAU would serve as a computation engine for a relatively low-powered microcontroller, and would enable complex code and encryption algorithms. Project will include implementation of a Reed Solomon encoder and decoder using the GFAU.

	\section{SPECIFICATION}

	\begin{enumerate}
		
		\item At a minimum, the GFAU shall handle inputs up to polynomial degree 8 (G(8)).
		\item The GFAU should handle inputs up to polynomial degree 16 (G(16)).
		\item The GFAU shall be implemented using FPGA.
		\item The GFAU shall provide addition, subtraction, multiplication, division, and logarithms within the context of Galois Fields.
		\item The GFAU shall be able to generate lookup tables for each operation in (4) given an irreducible polynomial.
		\item The GFAU should be able to determine if an input polynomial is reducible or not.
		\item The total cost should be under \$400.




	\end{enumerate}



\end{document}
