%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Contract
% LaTeX Template
% Version 1.0 (December 8 2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Brandon Fryslie
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Authors:
% Sabbir Ahmed, Jeffrey Osazuwa, Howard To, Brian Weber
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[paper=usletter, fontsize=12pt]{article}
\usepackage{amssymb}
\input{structure.tex} % specifies the document layout and style

\newcommand{\team}{Galois Field Arithmetic Unit}
\newcommand{\Sabbir}{Sabbir Ahmed}
\newcommand{\Jeffrey}{Jeffrey Osazuwa}
\newcommand{\Howard}{Howard To}
\newcommand{\Brian}{Brian Weber}

%----------------------------------------------------------------------------------------

% document info command
\newcommand{\documentinfo}[5]{
    \begin{centering}
        \parbox{6.8in}{
        \begin{spacing}{1}
            \begin{flushleft}
                \begin{tabular}{l l}
                    #1 \\
                    #2 \\
                    #3 \\
                    #4 \\
                    #5 \\
                \end{tabular} \\
                \rule{\textwidth}{1pt}
            \end{flushleft}
        \end{spacing}
        }
    \end{centering}
}

\begin{document}

    \documentinfo{\textbf{MEMO:} TSR-08}{\textbf{DATE: }{\today}}{\textbf{TO: } EFC LaBerge}{\textbf{FROM: }\Sabbir, \Jeffrey, \Howard, \Brian}{\textbf{SUBJECT: } Team Status Report}

    \vspace{-0.3in}
    \section{Introduction}
   The  Galois  Field  Arithmetic  Unit  will  accept  two  inputs $a$  and $b$  and  determine  the  desired arithmetic result $n$, and to establish the field generating polynomial.  The unit would serve as a computation engine for a relatively low-powered microcontroller, and would enable complex code and encryption algorithms.  Project will include implementation of a Reed Solomon en-coder and decoder using the GFAU. The purpose of this report is to detail the progress of the GFAU in the period of March 9, 2018 through April 6, 2018. This is the third status report for the second semester for the GFAU team.


    \section{Completed Tasks}
    During this work period, the team has continued to make progress on the GFAU. Including the following achievements:
    \begin{enumerate}

        \item Implemented 90\% of the modules
        \item Generated test benches for all the modules
        \item Parameterized all existing modules
        \item Optimized several modules to significantly reduce hardware

    \end{enumerate}
    The team has also worked on preparing the poster presentation for URCAD.

    \section{Planned Tasks}
    \begin{enumerate}

        \item Finish interfacing FPGA with memory
        \item Finalize all VHDL modules
        \item Interface FPGA with IO.
        \item Present the poster in URCAD

    \end{enumerate}


    \section{Current Issues}
  No issues, whether team dynamics or lack of resources.

\end{document}